Automating Free Logic in HOL, with an Experimental Application in Category Theory

### 2017-04-29 FreeLogic/2017-Journal/article.tex
update

Our exploration has been significantly supported by series of
experiments in which automated reasoning tools have been called from
within the proof assistant Isabelle/HOL via the
Sledgehammer tool \cite{Sledgehammer}. Moreover, we have obtained
very useful feedback at various stages from the model finder Nitpick
\cite{Nitpick} saving us from making several mistakes.

@@

Figure \ref{pic1} displays (parts of) the embedding of $\FFOL$ in
$\HOL$, encoded in Isabelle/HOL, that we have employed in our
experiments. A related Isabelle/HOL encoding of the above theory with
description has been presented and discussed in
\cite{ICMS}.\footnote{In the remainder of this article, and inline
  with our text so far,  we present the formulas of
  $\FFOL$ in non-boldface font. These formulas have been encoded in Isabelle/HOL using the
  abbreviations as introduced in Fig.~\ref{pic1}. In the actual source
  encoding, however, the usage of boldface and non-boldface is
  (for technical reasons) reversed.}

\begin{figure}[htp]
 \includegraphics[width=\textwidth]{EmbeddingPic}
 \caption{Isabelle/HOL encoding of $\FFOL$ (without description)\label{pic1}}
\end{figure}

>>>>

Our exploration has been significantly supported by series of
experiments in which automated reasoning tools have been called from
within the proof assistant Isabelle/HOL via the
Sledgehammer tool. Moreover, we have obtained
very useful feedback at various stages from the model finder Nitpick
\cite{Nitpick} saving us from making several mistakes.

@@

Figure \ref{pic1} displays (parts of) the embedding of $\FFOL$ in
$\HOL$, encoded in Isabelle/HOL, that we have employed in our
experiments. Excerpts of these experiments are illustrated in Fig.~\ref{pic2}. A related Isabelle/HOL encoding of the above theory with
description has been presented and discussed in
\cite{ICMS}.\footnote{In the remainder of this article, and inline
  with our text so far,  we present the formulas of
  $\FFOL$ in non-boldface font. These formulas have been encoded in Isabelle/HOL using the
  abbreviations as introduced in Fig.~\ref{pic1}. In the actual source
  encoding, however, the usage of boldface and non-boldface is
  (for technical reasons) reversed.}

\begin{figure}[htp]
 \includegraphics[width=\textwidth]{FFOL-Pic1}
 \caption{Isabelle/HOL encoding of $\FFOL$ (without description)\label{pic1}}
\end{figure}

\begin{figure}[htp]
 \includegraphics[width=\textwidth]{FFOL-Pic2}
 \caption{Encoding of Axioms Set V in Isabelle/HOL utilizing the
   embedded logic $\FFOL$ \label{pic2}}
\end{figure}
